---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  echo = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

This document guides contributors. It extends
[README](https://github.com/2DegreesInvesting/pactaCore/blob/main/README.md)
focusing on how this R package differs form a standard one.

* Some environment variables are convenient or required. A good place to set
them is in a project-specific .Renviron file, e.g.:

```{r}
writeLines(readLines(here::here(".Renviron")))
```

* pactaCore must be a sibling of a number of repositories. Clone them from
2DII's GitHub organization and ensure your local clones are up to date with the
repos on GitHub (to manage all siblings at once see `pacta-pull-origin-master`
in [`pacta-cli`](https://github.com/2DegreesInvesting/pacta-cli)).

```{r}
writeLines(paste0(
    "git clone git@github.com:2DegreesInvesting/", pactaCore:::siblings(), ".git"
))
```

* Git ignores all files under the directory tests/testthat/_snaps/ to avoid
leaking private data. Re-include public snapshots in .gitignore with a negation
pattern (!), e.g.:

```{r}
lines <- readLines(here::here(".gitignore"))
writeLines(grep("testthat/_snaps", lines, value = TRUE))
```

* Git ignores the directory tests/testthat/private/. Use it to store regression
references or other private data.

```{r}
fs::dir_tree(here::here("tests", "testthat", "private"))
```

You may compare two lists of reference datasets with the internal function
`compare_full()`.
