---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pactaCore

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of pactaCore is run the core steps of the [PACTA
methodology](https://2degrees-investing.org/resource/pacta/) with a single
command, in a reproducible way.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/pactaCore")
```

## Setup

A good setup for a pacta project looks like this:

```
pacta/
├── .env
├── input
│   ├── TestPortfolio_Input.csv
│   └── TestPortfolio_Input_PortfolioParameters.yml
└── output/

pacta-data/
|
...
```

* The .env file defines the paths to the output/, input/ and pacta-data/
directories. Here's mine:

```{bash, echo=FALSE, comment=""}
cat .env | sort
```

* The input/ directory must contain portfolio files like
[TestPortfolio_Input.csv](https://github.com/2DegreesInvesting/pactaCore/blob/master/working_dir/20_Raw_Inputs/TestPortfolio_Input.csv),
and parameters files like
[TestPortfolio_Input_PortfolioParameters.yml](https://github.com/2DegreesInvesting/pactaCore/blob/master/working_dir/10_Parameter_File/TestPortfolio_Input_PortfolioParameters.yml).

* The output/ directory can be empty.

* The pacta-data/ directory can be cloned from its private GitHub repository
(provided you have access) with:

```bash
git clone git@github.com:2DegreesInvesting/pacta-data.git  # Private data!
```

Typically the .env file, and the input/ and output/ directories all live under
the same parent directory (e.g. pacta/), while the pacta-data/ directory lives
elsewhere.

<details> 

Each corresponding `<pair-name>` the portfolio and parameter files must be named
`<pair-name>_Input.csv` and `<pair-name>_Input_PortfolioParameters.yml`,
respectively. For example:

  * This pair is valid: `a_Input.csv`, `a_Input_PortfolioParameters.yml`.
  
  * This pair is invalid: `a_Input.csv`, `b_Input_PortfolioParameters.yml`.

In the parameter files, whatever values you give to `portfolio_name_in` and
`investor_name_in` will populate the columns `portfolio_name` and
`investor_name` of some output files. For example:

* A parameter file:

```r
default:
    parameters:
        portfolio_name_in: TestPortfolio_Input
        investor_name_in: Test
        peer_group: pensionfund
        language: EN
        project_code: CHPA2020
```

* A few rows of some relevant output files and columns:

```r
$Bonds_results_company.rda
       portfolio_name investor_name
1 TestPortfolio_Input          Test
2 TestPortfolio_Input          Test
3 TestPortfolio_Input          Test

$Bonds_results_map.rda
       portfolio_name investor_name
1 TestPortfolio_Input          Test
2 TestPortfolio_Input          Test
3 TestPortfolio_Input          Test

$Bonds_results_portfolio.rda
       portfolio_name investor_name
1 TestPortfolio_Input          Test
2 TestPortfolio_Input          Test
3 TestPortfolio_Input          Test
```

</details>




## Example

```{r example}
library(pactaCore)
```

Use `run_pacta_core()` with an environment file, or default to ".env" under the
working directory.

```r
run_pacta_core()
```

* The output/ directory should now look like this:

```bash
output
└── working_dir
    ├── 00_Log_Files
    │   └── TestPortfolio_Input
    ├── 10_Parameter_File
    │   └── TestPortfolio_Input_PortfolioParameters.yml
    ├── 20_Raw_Inputs
    │   └── TestPortfolio_Input.csv
    ├── 30_Processed_Inputs
    │   └── TestPortfolio_Input
    │       ├── audit_file.csv
    │       ├── audit_file.rda
    │       ├── bonds_portfolio.rda
    │       ├── coveragegraph.json
    │       ├── coveragegraphlegend.json
    │       ├── coveragetextvar.json
    │       ├── emissions.rda
    │       ├── equity_portfolio.rda
    │       ├── fund_coverage_summary.rda
    │       ├── invalidsecurities.csv
    │       ├── invalidsecurities.json
    │       ├── overview_portfolio.rda
    │       ├── portfolio_weights.json
    │       └── total_portfolio.rda
    ├── 40_Results
    │   └── TestPortfolio_Input
    │       ├── Bonds_results_company.rda
    │       ├── Bonds_results_map.rda
    │       ├── Bonds_results_portfolio.rda
    │       ├── Equity_results_company.rda
    │       ├── Equity_results_map.rda
    │       └── Equity_results_portfolio.rda
    └── 50_Outputs
        └── TestPortfolio_Input
```

<details>
<summary>For developers</summary>

When developing pactaCore, you may define `PACTA_*` directories in a
project-specific `.Renviron`. Here is mine:

```bash
PACTA_INPUT=/home/mauro/git/pacta/input
PACTA_OUTPUT=/home/mauro/git/pacta/output
PACTA_DATA=/home/mauro/git/pacta-data
```

You can then setup persistent IO directories with `create_pacta()`, e.g.:

```r
devtools::load_all()
create_pacta("/home/mauro/git/pacta")
```

For ephemeral IO directories see `local_pacta()`.

</details>
