---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "",
  echo = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
# The code that uses fs is hidden to keep instructions short
library(fs)
library(pactaCore)
```

# pactaCore

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of pactaCore is run the core steps of the [PACTA
methodology](https://2degrees-investing.org/resource/pacta/) with a single
command, in a reproducible way.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/pactaCore")
```

## Setup

A good setup for a pacta project looks like this:

```{r}
pacta <- path_home("pacta_tmp")
example_inputs <- dir_ls(
  system.file("extdata", package = "pactaCore"),
  regexp = "Input"
)
create_pacta(pacta, input_paths = example)

dir_tree(pacta, all = TRUE)
```

```r
#> path/to/private/pacta-data/
#> ├── ...
#> ...
```

* The .env file locates the input/, output/, and pacta-data/ directories, e.g.:

```{r}
env <- path(pacta, ".env")
writeLines(readLines(env))
```

* The input/ directory must contain portfolio files like
[TestPortfolio_Input.csv](https://github.com/2DegreesInvesting/pactaCore/blob/master/working_dir/20_Raw_Inputs/TestPortfolio_Input.csv),
and parameters files like
[TestPortfolio_Input_PortfolioParameters.yml](https://github.com/2DegreesInvesting/pactaCore/blob/master/working_dir/10_Parameter_File/TestPortfolio_Input_PortfolioParameters.yml).

* The output/ directory typically starts empty.

* The pacta-data/ directory is private. With permission get if from GitHub with:

```bash
# From the terminal
git clone git@github.com:2DegreesInvesting/pacta-data.git
```

## Usage

Use the pactaCore package with `library()` and `run_pacta()` with your
environment file.

```{r echo=TRUE, comment="#>"}
library(pactaCore)

(env <- file.path(pacta, ".env"))
run_pacta(env)
```

The output/ directory is now populated with results:

```{r}
dir_tree(pacta)
```

<details> 

For each corresponding `<pair-name>`, the portfolio and parameter files must be
named `<pair-name>_Input.csv` and `<pair-name>_Input_PortfolioParameters.yml`,
respectively. For example:

  * This pair is valid: `a_Input.csv`, `a_Input_PortfolioParameters.yml`.
  
  * This pair is invalid: `a_Input.csv`, `b_Input_PortfolioParameters.yml`.

In the parameter files, whatever values you give to `portfolio_name_in` and
`investor_name_in` will populate the columns `portfolio_name` and
`investor_name` of some output files. For example:

* A parameter file:

```{r}
writeLines(readLines(example_inputs[[2]]))
```

* A few rows of some relevant output files and columns:

```{r}
paths <- fs::dir_ls(pactaCore:::results_path(pacta))
datasets <- lapply(paths, readRDS)
```

```{r}
lapply(datasets, function(x) head(x[c("portfolio_name", "investor_name")]))
```

</details>

```{r echo=FALSE}
dir_delete(pacta)
```
