---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
# The code that uses fs is hidden to keep instructions short
library(fs)
library(pactaCore)
```

# pactaCore

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/pactaCore/workflows/R-CMD-check/badge.svg)](https://github.com/2DegreesInvesting/pactaCore/actions)
<!-- badges: end -->

The goal of pactaCore is run the core steps of the [PACTA
methodology](https://2degrees-investing.org/resource/pacta/) with a single
command, in a reproducible way.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/pactaCore")
```

## Using PACTA to get results for one or more portfolios

As usual, use pactaCore with `library()`. Here we also use other optional but
convenient packages.

```{r}
library(pactaCore)
library(fs)
```

### Setup

`create_pacta()` sets up a pacta project with a fake portfolio and parameter
file. For a real analysys you should replace the test portfolio and parameter files
with your own, and work not in a temporary directory but in a persistent one.

```{r}
pacta <- create_pacta(dir = tempfile("pacta"), data = "~/pacta-data")

dir_tree(pacta, all = TRUE)
```

* The .env file locates the input/, output/, and pacta-data/ directories.

```{r}
env <- path(pacta, ".env")
readLines(env)
```

* The input/ directory must contain portfolio files like
[TestPortfolio_Input.csv](https://github.com/2DegreesInvesting/pactaCore/blob/master/inst/extdata/TestPortfolio_Input.csv),
and parameters files like
[TestPortfolio_Input_PortfolioParameters.yml](https://github.com/2DegreesInvesting/pactaCore/blob/master/inst/extdata/TestPortfolio_Input_PortfolioParameters.yml).

* The output/ directory typically starts empty.

* The pacta-data/ directory is private. With permission get if from GitHub with:

```bash
# From the terminal
git clone git@github.com:2DegreesInvesting/pacta-data.git
```

### Run PACTA

`run_pacta()` runs PACTA on the project described by your .env file.

```{r}
run_pacta(env)
```

The output/ directory is now populated with results:

```{r echo=TRUE, comment="#>"}
dir_tree(path(pacta, "output"))
```

<details> 

For each corresponding `<pair-name>`, the portfolio and parameter files must be
named `<pair-name>_Input.csv` and `<pair-name>_Input_PortfolioParameters.yml`,
respectively. For example:

  * This pair is valid: `a_Input.csv`, `a_Input_PortfolioParameters.yml`.
  
  * This pair is invalid: `a_Input.csv`, `b_Input_PortfolioParameters.yml`.

In the parameter files, whatever values you give to `portfolio_name_in` and
`investor_name_in` will populate the columns `portfolio_name` and
`investor_name` of some output files. For example:

* A parameter file:

```{r}
writeLines(readLines(example_input_paths()[[2]]))
```

* A few rows of some relevant output files and columns:

```{r echo=FALSE}
paths <- fs::dir_ls(pactaCore:::output_results_path(pacta))
datasets <- lapply(paths, readRDS)
```

```{r echo=FALSE}
lapply(datasets, function(x) head(x[c("portfolio_name", "investor_name")]))
```

</details>

## Related projects

pactaCore is an experimental alternative to a part of
[PACTA_analysis](https://github.com/2DegreesInvesting/pacta_analysis) -- which
as of this writing continues to be the main line of development.
