---
title: "pactaCore for developers"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This article aims software developers. Its gosl is to advertise aspects of
pactaCore that may be valuable but not obvious. It assumes you already know how
to use pactaCore for data analysis (see README), and how to setup your
development environment (see
[CONTRIBUTING](https://github.com/2DegreesInvesting/pactaCore/blob/main/.github/CONTRIBUTING.md)).

## Setup

README provides a gentle explanation of the setup. Here we do it quickly:

* Use pactaCore and other optional but convenient packages.

```{r}
library(pactaCore)
library(fs)
library(here)

show <- function(path) writeLines(readLines(path))
```

* Setup a pacta project with a fake portfolio and parameter files at a temporary
directory.

```{r}
pacta <- create_pacta(dir = tempfile("pacta"), data = "~/pacta-data")

dir_tree(pacta, all = TRUE)
```

## Uses

### Using pactaCore to test and refactor PACTA_analysis

pactaCore can help you test and refactor PACTA_analysis -- specifically web_tool
scripts 1 and 2. Here is how:

* Ensure your ".env" file includes the variable `PACTA_ANALYSIS`, giving the
path to the local copy of PACTA_analysis you want to use as a reference -- e.g.
because its `HEAD` points to the latest commit on `master`.

```{r}
env <- path(pacta, ".env")
lines <- unique(c(readLines(env), "PACTA_ANALYSIS=~/PACTA_analysis"))
writeLines(lines, env)

show(env)
```

* Modify the web tool scripts 1 and 2 in a different local clone of
PACTA_analysis, and create a vector giving the path to the modified scripts.

```{r}
scripts <- path("~/git/PACTA_analysis", paste0("web_tool_script_", 1:2, ".R"))
scripts
```

* Working from pactaCore, run `update_pacta_legacy()`.

```{r}
here::here()

update_pacta_legacy(scripts)
```

* Run `devtools::test()`. If the changes you made to the web tool scripts 
changed the structure of the resulting datasets, then you may already get a
failing test.

```r
devtools::test()
```

* If the previous tests passed, run `compare_full()` to test for more subtle
differences.

```r
compare_full()
```

### Using pactaCore to benefit from its testing infrastructure

Above you saw how to run regression tests against a reference PACTA_analysis
repo. This section covers other more general uses of the testing infrastructure
that pactaCore provides.

* Some tests are slow. You may skip them wiht `test_fast()` and `check_fast()`.

* Git ignores all files under the directory tests/testthat/_snaps/ to avoid
leaking private data. Re-include public snapshots in .gitignore with a negation
pattern (!), e.g.:

```{r}
lines <- readLines(here(".gitignore"))
writeLines(grep("testthat/_snaps", lines, value = TRUE))
```

* Git ignores the directory tests/testthat/private/. Use it to store regression
references or other private data.

```{r}
dir_tree(here("tests", "testthat", "private"))
```

### Using pactaCore to benefit from error messages

The required setup for pactaCore is enforced with assertions that should help
you figure out what's wrong and how to fix it.

```{r}
# Setup
bad_pacta <- create_pacta(dir = tempfile("bad_pacta"), data = "~/pacta-data")
env <- path(bad_pacta, ".env")
# Degrade .env to show how we handle errors
writeLines(sub("^PACTA_INPUT.*", "", readLines(env)), env)
readLines(env)

try(run_pacta(env))

# Set the environment variable but incorrectly
writeLines("PACTA_INPUT=/bad/path", env)

try(run_pacta(env))
```

### Using pactaCore to access a dockerized computing environment

You can access a dockerized computing environment in four steps:

1. Install `docker`.

2. Install `docker-compose`.

3. Clone pactaCore and make it your working directory.

4. Ensure your ".env" file sets the `PASSWORD` to login to RStudio.

```{r}
show(here(".env"))
```

5. Run `docker-compose up`.

Rstudio is now available from your web browser at localhost:8787. Login with
username "rstudio" and your password.

In the container, the required directories will be mounted under /home/rstudio,
and discovered via the file ".env_rstudio":

```{r}
show(here(".env_rstudio"))
```
